CUNY SPSS Data Science Math Homework 3

### 2018-07-27 data-science-math/Homework 3.Rmd
More work

Lower Bound: **0.153**

Upper Bound: **0.187**

```{r}
ci <- 0.98
m <- N * p
sdm <- sqrt(N*p*(1-p))

df <- (N-n) - 1
t <- qt(ci, df)
round((m-t*sdm)/N, 3)
round((m+t*sdm)/N, 3)
```

@@

Lower Bound: **0.294**

Upper Bound: **0.365**

```{r}
ci <- .95
m <- N * p
sdm <- sqrt(N*p*(1-p))

df <- (N-n) - 1
t <- qt(ci, df)
round((m-t*sdm)/N, 3)
round((m+t*sdm)/N, 3)
```

>>>>

Lower Bound: **0.151**

Upper Bound: **0.189**

```{r}
ci <- 0.98
m <- N * p
sdm <- sqrt((p*(1-p))/n)
df <- (N-n) - 1
t <- qt(ci, df)
round(p-t*sdm, 3)
round(p+t*sdm, 3)
```

@@

Lower Bound: **0.267**

Upper Bound: **0.391**

```{r}
ci <- .95
m <- N * p
sdm <- sqrt((p*(1-p))/n)
df <- (N-n) - 1
t <- qt(ci, df)
round(p-t*sdm, 3)
round(p+t*sdm, 3)
```
